Antigenic phenotypes and phylogenetic metrics improve forecasts of seasonal influenza A/H3N2 evolution

### 2020-08-03 manuscript/tables/model_summary.tex
Use eLife template and citation styles
Updates most citations to use the parenthetical form, adds the eLife document
type and bibliography style, updates the model summary table to use the full
citation style, and adds a citation for Barrat-Charlaix et al. 2020 which is now
available as a preprint.

\begin{tabular*}{1.4\textwidth}{lllll}
\toprule
Model                                                        & Populations        & Data type             & Fitness category      & Originally implemented by                   \\
\midrule
true fitness                                                 & simulated          & simulated populations & positive control      & this study                      \\
naive                                                        & simulated, natural & HA sequences          & negative control      & this study                      \\
epitope antigenic novelty                                    & simulated, natural & HA sequences          & antigenic drift       & {\L}uksza and L\"assig \cite{Luksza:2014hj} \\
epitope ancestor                                             & simulated, natural & HA sequences          & antigenic drift       & {\L}uksza and L\"assig \cite{Luksza:2014hj} \\
HI antigenic novelty                                         & natural            & serological assays    & antigenic drift       & this study                      \\
mutational load                                              & simulated, natural & HA sequences          & functional constraint & {\L}uksza and L\"assig \cite{Luksza:2014hj} \\
\makecell{deep mutational scanning (DMS) \\ mutational effects} & natural            & DMS assays            & functional constraint & Lee et al. 2018 \cite{Lee2018}              \\
local branching index (LBI)                                  & simulated, natural & HA sequences          & clade growth          & Neher et al. 2014 \cite{Neher:2014eu}       \\
delta frequency                                              & simulated, natural & HA sequences          & clade growth          & this study                      \\
\bottomrule
\end{tabular*}

>>>>

\begin{tabular*}{1.4\textwidth}{lllll}
\toprule
Model                                                        & Populations        & Data type             & Fitness category      & Originally implemented by                   \\
\midrule
true fitness                                                 & simulated          & simulated populations & positive control      & this study                      \\
naive                                                        & simulated, natural & HA sequences          & negative control      & this study                      \\
epitope antigenic novelty                                    & simulated, natural & HA sequences          & antigenic drift       & \cite{Luksza:2014hj} \\
epitope ancestor                                             & simulated, natural & HA sequences          & antigenic drift       & \cite{Luksza:2014hj} \\
HI antigenic novelty                                         & natural            & serological assays    & antigenic drift       & this study                      \\
mutational load                                              & simulated, natural & HA sequences          & functional constraint & \cite{Luksza:2014hj} \\
\makecell{deep mutational scanning (DMS) \\ mutational effects} & natural            & DMS assays            & functional constraint & \cite{Lee2018}              \\
local branching index (LBI)                                  & simulated, natural & HA sequences          & clade growth          & \cite{Neher:2014eu}       \\
delta frequency                                              & simulated, natural & HA sequences          & clade growth          & this study                      \\
\bottomrule
\end{tabular*}
